---
title: "Assignment B-1: Making a function"
output: github_document
---

# Setup
Load data and needed package:
```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(arsenal)
library(broom)
library(testthat)
```

# Exercise 1: Make a Function (25 points)
Here I create a function that retrieves the standard error of a linear model object fitted for two numeric vectors.
```{r, message = FALSE}
#' @description
#' This function will return the standard error of the fitted linear model for vector x, y. Since we are fitting a linear model, value that's not numeric will not be accepted, also we would expect the length of these two vectors to match. The input vector can have NA as long as we have enough numeric elements to fit our model.
#'
#' @title lm_std function
#' @param x - corresponds to is the "X" vector that we want to fit our linear regression model for, 
#' @param y - corresponds to is the "Y" vector that we want to fit our linear regression model for
#' @param dataset - the dataset that contains the x, y variable, this dataset variable is set as an empty vector by default if the user wishes to input two vector x, y directly.
#' @return return the standard error of the fitted linear model for vector x, y.
#'
lm_std <- function( x, y, dataset=c()) {
    stopifnot(is.numeric(x) && is.numeric(y))
    stopifnot(length(x) == length(y))
    my_lm <- lm(y ~ x, data = dataset)
    tidy_lm <- tidy(my_lm)
    tidy_lm$std.error[2]# 2 is for extracting the standard error row corresponding to our x variable
}

```

# Exercise 2: Document your Function (20 points)

In the same code chunk where you made your function, document the function using roxygen2 tags.

Documentation added in code chunk accordingly.

# Exercise 3: Include examples (15 points)
Demonstrate the usage of your function with a few examples. Use one or more new code chunks, describing what you’re doing.\

## Example 1:

Here I want to use this function to fit a linear model between variable *perimeter_mean* and *radius_mean* in dataset *cancer_sample*.
```{r, message = FALSE}
cancer_lm <- lm(perimeter_mean ~ radius_mean, data = cancer_sample)
sum_cancer <- summary(cancer_lm)
sum_cancer$coefficients
```

So I would expect the function to return 0.01895491.\
```{r, message = FALSE}

print(lm_std(cancer_sample$radius_mean, cancer_sample$perimeter_mean, cancer_sample))
```


Which means this function works.

## Example 2:

Now let's try using two numeric vectors.\
```{r, message = FALSE}
x1 <- c(1,2,3)
y1 <- c(4,5,7)
lm_1 <- lm(y1~x1)
summary(lm_1)$coefficients
```

```{r, message = FALSE}
print(lm_std(x1,y1))
```

Which means this function works for two vector input as well.

## Example 3:

Now let's try using two vectors with different length, we should expect an error of length not matching in this one.
```{r, message = FALSE, error = TRUE}
x2 <- c(1,2,3,4)
y2 <- c(4,5,7)
print(lm_std(x2, y2))
```

Which is as expected.

# Exercise 4: Test the Function (25 points)

Write formal tests for your function. You should use at least three non-redundant uses of an expect_() function from the testthat package, and they should be contained in a test_that() function (or more than one). They should all pass.

## Test1:

Get input vectors from dataset with no NA's\
```{r, message = FALSE, error = FALSE}
test1_lm <- lm(area_mean ~perimeter_mean, cancer_sample)
result1 <- tidy(test1_lm)$std.error[2]

test_that("Test 1:", {
  expect_equal(result1, lm_std(cancer_sample$perimeter_mean ,cancer_sample$area_mean, cancer_sample))
})
```
## Test2:

Directly input numeric vectors with matching length and no NA's\
```{r, message = FALSE, error = FALSE}
test2_lm <- lm(c(2,4,6) ~c(5,7,10))
result2 <- tidy(test2_lm)$std.error[2]

test_that("Test 2:", {
  expect_equal(result2, lm_std(c(5,7,10), c(2,4,6)))
})
```

## Test3:

Directly input numeric vectors with matching length that has NA.

```{r, message = FALSE, error = FALSE}
test3_lm <- lm(c(2,4,6,8) ~c(5,7,10,NA))
result3 <- tidy(test2_lm)$std.error[2]

test_that("Test 3:", {
  expect_equal(result3, lm_std(c(5,7,10,NA),c(2,4,6,8)))
})
```

## Test4:

Directly input numeric vectors with matching length that has special character.\
```{r, message = FALSE, error = TRUE}
test_that("Test 4:", {
  expect_error(lm_std(c(5,7,9,11), c(2,4,6,"s")), 'is.numeric')
})
```
## Test5:

Directly input numeric vectors with different length.

```{r, message = FALSE, error = TRUE}
test_that("Test 5:", {
  expect_error(lm_std(c(5,7,9,11,13), c(2,4,5,8)))
})
```