---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LinearModelSE

<!-- badges: start -->
<!-- badges: end -->
The goal of LinearModelSE is to take in two numeric vectors x and y, either manually or get two vectors from a dataset, and return the standard error of the linear model fitted for vector x, y. Since it's for fitting a linear model, the length of x and y should be the same.

## Installation

You can install the development version of LinearModelSE like so:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-MengyaZeng/LinearModelSE", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(LinearModelSE)
## you can either directly input two numeric vectors 
lm_std(c(1,2,3), c(4,5,7))
## or get two vectors from a dataset
lm_std(datateachr::cancer_sample$radius_mean, datateachr::cancer_sample$perimeter_mean)
```


